dendro

### 2017-05-26 analysis/test-bai.Rmd
update correlation coefficient

```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

chrono_bai <- function(bai_object, alpha){ 
  require(dplyr)

  b <- bai_object 
  alpha <- as.numeric(alpha)

@@

c_sj <- chrono_bai(bai_sj, alpha=0.75)

c_sj

@@

>>>>

```{r, echo=FALSE}
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

chrono_bai <- function(bai_object){ 
  require(dplyr)

  b <- bai_object 
  # alpha <- as.numeric(alpha)

@@

cro_sj <- chrono_bai(bai_sj)
cro_sj$level <- 'SJ'
cro_ca <- chrono_bai(bai_ca)
cro_ca$level <- 'CA'

# San JUan 
cro_sjH <- chrono_bai(bai_sjH)
cro_sjH$site <- 'SJ_High'

cro_sjL <- chrono_bai(bai_sjL)
cro_sjL$site <- 'SJ_Low'

cro_sj<- rbind(cro_sjH, cro_sjL)
cro_sj$loc <- 'Norte (San Juan)'

cro %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + scale_colour_manual(values = c("red", "blue")) + 
  theme(panel.grid = element_blank())

# Canar 
cro_caH <- chrono_bai(bai_caH)
cro_caH$site <- 'CA_High'
te <- chrono_bai(bai_caH)
plot.crn(te)
plot(te)
plot(te, add.spline=TRUE, nyrs=30)

cro_caL <- chrono_bai(bai_caL)
cro_caL$site <- 'CA_Low'

cro_ca <- rbind(cro_caH,cro_caL)
cro_ca$loc <- 'Sur (Canar)'

cro_ca %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + scale_colour_manual(values = c("red", "blue")) + 
  theme(panel.grid = element_blank())

cro_sites <- rbind(cro_ca, cro_sj)

cro_sites %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + 
  theme(panel.grid = element_blank()) + facet_wrap(~loc, nrow = 2) + 
  scale_colour_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) + 
  geom_smooth(method= 'loess', span = 0.75, se=FALSE)

 + 
geom_smooth(method= 'loess', span = 0.75, se=FALSE)

  geom_ribbon(aes(x= year, 
                  ymin = loess_fit - 1.96*loess_se,
                  ymax = loess_fit + 1.96*loess_se), na.rm = FALSE, 
              fill = "grey") +
c_sj

@@

```{r}
# centred moved average smooth
# https://cran.r-project.org/web/packages/smooth/vignettes/sma.html

correla_cronos <- function(cronologia, win_vector, crononame){

  cro_object <- cronologia

  # Set bai and years variables 
  bai <- cro_object[,'bai_mean']
  yearss <- cro_object[,'year']

  # object to store 
  out <- c()

  for (i in seq_along(win_vector)){ 
    # moving window size 
    f <- rep(1/i, i)

    # moving average smooth 
    bai_smooth <- stats::filter(bai, f, sides=1)

    # out 
    out_aux <- as.data.frame(cbind(yearss, bai_smooth))

    out_aux$size_wind <- i
    out <- rbind(out, out_aux)
  }
  out$crononame <- crononame 
  out
}

correla_cro_caH <- correla_cronos(cro_caH, win_vector=seq(1,40, by=1), crononame = 'cro_caH')
correla_cro_caL <- correla_cronos(cro_caL, win_vector=seq(1,40, by=1), crononame = 'cro_caL')
correla_cro_sjH <- correla_cronos(cro_sjH, win_vector=seq(1,40, by=1), crononame = 'cro_sjH')
correla_cro_sjL <- correla_cronos(cro_sjL, win_vector=seq(1,40, by=1), crononame = 'cro_sjL')

correla_croSJ <- rbind(correla_cro_sjH, correla_cro_sjL)

# SJ 
out_final <- c()

for (j in 1:40){

  aux <- correla_croSJ %>% 
    filter(size_wind == j) %>%
    select(-size_wind) %>% 
    spread(crononame, bai_smooth) %>% 
    as.data.frame()

  rownames(aux) <- aux$yearss 
  aux1 <- aux[,-1]

  output_correla <- interseries.cor(aux1)

  out <- as.data.frame(cbind(res.cor = output_correla$res.cor[1], 
                           p_val = output_correla$p.val[1]))

  out$size <- j

  out_final <- rbind(out_final, out)

  }

out_final$site <- 'SJ'

correla_final_sj <- out_final

# CA
correla_croCA <- rbind(correla_cro_caH, correla_cro_caL)
out_final <- c()

for (j in 1:40){

  aux <- correla_croCA %>% 
    filter(size_wind == j) %>%
    select(-size_wind) %>% 
    spread(crononame, bai_smooth) %>% 
    as.data.frame()

  rownames(aux) <- aux$yearss 
  aux1 <- aux[,-1]

  output_correla <- interseries.cor(aux1)

  out <- as.data.frame(cbind(res.cor = output_correla$res.cor[1], 
                           p_val = output_correla$p.val[1]))

  out$size <- j

  out_final <- rbind(out_final, out)

  }

out_final$site <- 'CA'

correla_final_ca <- out_final

correla_finales <- rbind(correla_final_ca, correla_final_sj)
correla_finales %>% 
  ggplot(aes(x=size, y=res.cor, colour=site)) + geom_line()+
  theme_bw() + 
  ylab('Correlation coefficient') + xlab('years(smooth)') + geom_smooth(method = 'loess', se=FALSE)

c11 <- c1[26:nrow(c1),]

cor(c11$cro_sjH, c11$cro_sjL)

ggplot(c1, aes(x=yearss, y=cro_sjH)) + geom_line() + 
  geom_line(aes(x=yearss, y=cro_sjL), colour='blue')

cronologia <- cro_caH
cro_object <- get()
cro_object <- get(cronologia)

plot(cro_caH$year, cro_caH$bai_mean, type='l')
lines(cro_caH$year, y_lag, col="blue")

  y_lag <- filter(y, f20, sides=1)
lines(x, y_lag, col="red")

# average of current sample and 19 previous samples (red)
f20 <- rep(1/20, 20)
f20
#>  [1] 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05
#> [18] 0.05 0.05 0.05
